---
title: "Performance Update"
author: "Matt Barry"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: beamer_presentation
params:
  quandl_api:
    value: NA
---

```{r,echo=FALSE,cache=FALSE,warning=FALSE,message=FALSE}
ignore <- lapply(
  c("knitr",
    "ggplot2",
    "quantmod",
    "PerformanceAnalytics",
    "Quandl",
    "directlabels",
    "scales"),
    require,
  quietly=TRUE,warn.conflicts=FALSE,character.only=TRUE)

options("getSymbols.warning4.0"=FALSE,
        replace.assign=TRUE,
        width=80)
start_date <- "2012-01-01"
current_date <- Sys.Date()
exchange_file <- paste0(paste("exchange",current_date,sep='-'),".RData")
start_time <- date()
stroke_size = 0.75

knitr::opts_chunk$set(
  echo = FALSE,
  tidy = FALSE,
  cache = TRUE,
  warning = FALSE,
  out.width='0.85\\linewidth',
  size='scriptsize',
  fig.path='figure/relpof-',
  fig.keep='last',
  fig.align='center',
  results='hide',
  message = FALSE)

`%nin%` <- Negate(`%in%`)

quandl_api <- params$quandl_api
if (is.na(quandl_api) || ("NA" == quandl_api)) {
   quandl_api <- Sys.getenv("QUANDL_API")
}
Quandl.api_key(quandl_api) # authenticate

# use the adjusted values from quandl
getAdjusted <- function(qd, na.fill=TRUE) {
  mstring <- "Adj_"
  rv <- qd
  if ( any( grepl(mstring, colnames(qd))) ) {
    rv <- qd[,which(grepl(mstring, colnames(qd)))]
    if ( na.fill == TRUE ) {
      if ( any( is.na(rv)) ) {
        rv <- na.approx(rv)        
      }
    }
    colnames(rv) <- gsub(mstring,"",colnames(rv))
  }
  rv
}
```

```{r tickers}
macro_tickers <- c("SPY","EEM","ELD","GLD","GSG","UUP","VNQ","TLT","AGG")
bull_tickers <- c("AGG","DVY","FLTB","GLD","GSG","SHV")
bear_tickers <- c("SPY","GSG","GLD","FXF","FUTY","FLTB","TLT")
basket_tickers <- c("VTI","VGK","EWJ","EEM","IEF","ICF","RWX","DBC","GLD","TLT")
index_tickers <- c("^GSPC")

all_symbols <- sort(unique(c(
                             macro_tickers,
			                       bull_tickers,
                             bear_tickers,
                             basket_tickers,
			                       index_tickers
                             )))
exchange_data <- new.env()
missing_tickers <- c()
if ( file.exists( exchange_file )) {
  load( exchange_file ) # loads exchange data environment
  missing_tickers <- get("missing_tickers",envir=exchange_data)
} else {
  # Quandl
  for ( s in seq_along(all_symbols)) {
    symbol <- all_symbols[s]
    message(paste("Fetching",symbol))
    tryCatch({
      #getSymbols(symbol,
      #           from=start_date,
      #           adjust=TRUE,
      #           warnings = FALSE,
      #           env = exchange_data),
      x <- Quandl(paste0("EOD/",symbol),type="xts",order="asc",start_date=start_date)
      x <- getAdjusted(x)
    },
      error = function(e) {
        missing_tickers <<- c(missing_tickers,symbol)
      }
    )
  }
  
  # Quandl
  message("Fetching Quandl data")
  CCHA <- Quandl("CBOE/COMBINED_PC_ARCHIVE",type="xts",order="asc",start_date="1980-01-01")
  TPCA <- Quandl("CBOE/TOTAL_PC_ARCHIVE",type="xts",order="asc",start_date="1980-01-01")
  TPC <- Quandl("CBOE/TOTAL_PC",type="xts",order="asc",start_date="1980-01-01")
  VIX <- Quandl("CBOE/VIX",type="xts",order="asc",start_date=start_date)
  VXST <- Quandl("CBOE/VXST",type="xts",order="asc",start_date=start_date)
  VXMT <- Quandl("CBOE/VXMT",type="xts",order="asc",start_date=start_date)
  SKEW <- Quandl("CBOE/SKEW",type="xts",order="asc",start_date=start_date)
  LOVOL <- Quandl("CBOE/LOVOL",type="xts",order="asc",start_date=start_date)
  VXEEM <- Quandl("CBOE/VXEEM",type="xts",order="asc",start_date=start_date)
  GVZ <- Quandl("CBOE/GVZ",type="xts",order="asc",start_date=start_date)
  SPXPC <- Quandl("CBOE/SPX_PC",type="xts",order="asc",start_date=start_date)
  EQUITY_PC <- Quandl("CBOE/EQUITY_PC",type="xts",order="asc",start_date=start_date)
  INDEX_PC <- Quandl("CBOE/INDEX_PC",type="xts",order="asc",start_date=start_date)
  TOTAL_PC <- Quandl("CBOE/TOTAL_PC",type="xts",order="asc",start_date=start_date)
  MLAAOAS <- Quandl("ML/AAOAS",type="xts",order="asc",start_date=start_date)
  MLBOAS <- Quandl("ML/BOAS",type="xts",order="asc",start_date=start_date)
  MLHYOAS <- Quandl("ML/HYOAS",type="xts",order="asc",start_date=start_date)
  MLAAY <- Quandl("ML/AAY",type="xts",order="asc",start_date=start_date)
  MLBBY <- Quandl("ML/BBY",type="xts",order="asc",start_date=start_date)
  MLCCCY <- Quandl("ML/CCCY",type="xts",order="asc",start_date=start_date)

  assign("CCHA",CCHA,envir=exchange_data)
  assign("TPCA",TPCA,envir=exchange_data)
  assign("TPC",TPC,envir=exchange_data)
  assign("VIX",VIX,envir=exchange_data)
  assign("VXST",VXST,envir=exchange_data)
  assign("VXMT",VXMT,envir=exchange_data)
  assign("SKEW",SKEW,envir=exchange_data)
  assign("LOVOL",LOVOL,envir=exchange_data)
  assign("VXEEM",VXEEM,envir=exchange_data)
  assign("GVZ",GVZ,envir=exchange_data)
  assign("SPXPC",SPXPC,envir=exchange_data)
  assign("EQUITY_PC",EQUITY_PC,envir=exchange_data)
  assign("INDEX_PC",INDEX_PC,envir=exchange_data)
  assign("TOTAL_PC",TOTAL_PC,envir=exchange_data)
  assign("MLAAOAS",MLAAOAS,envir=exchange_data)
  assign("MLBOAS",MLBOAS,envir=exchange_data)
  assign("MLHYOAS",MLHYOAS,envir=exchange_data)
  assign("MLAAY",MLAAY,envir=exchange_data)
  assign("MLBBY",MLBBY,envir=exchange_data)
  assign("MLCCCY",MLCCCY,envir=exchange_data)

}
  
assign("missing_tickers",missing_tickers,envir=exchange_data)
save(exchange_data,file=exchange_file)

```

```{r prices}
available_symbols <- subset(all_symbols,all_symbols %nin% missing_tickers)

closing_prices <- do.call(cbind,
                          lapply(available_symbols,
                                 function(x) {
                                   Cl(get(gsub("^","",x,fixed=TRUE),envir=exchange_data))
                                 }))
closing_prices <- na.locf(closing_prices)
colnames(closing_prices) <- available_symbols
last_data_date <- xts::last(index(closing_prices))
```

```{r returns}
daily_returns <- closing_prices / stats::lag(closing_prices) - 1
daily_returns <- daily_returns[-1]
daily_returns[is.na(daily_returns)] <- 0
daily_returns_30 <- xts::last(daily_returns,"30 days")
daily_returns_60 <- xts::last(daily_returns,"60 days")
relative_tlt_30 <- Return.relative(daily_returns_30,daily_returns_30[,"TLT"])
relative_tlt_60 <- Return.relative(daily_returns_60,daily_returns_60[,"TLT"])
relative_spy_30 <- Return.relative(daily_returns_30,daily_returns_30[,"SPY"])
relative_spy_60 <- Return.relative(daily_returns_60,daily_returns_60[,"SPY"])
colnames(relative_tlt_30) <- colnames(daily_returns)
colnames(relative_tlt_60) <- colnames(daily_returns)
colnames(relative_spy_30) <- colnames(daily_returns)
colnames(relative_spy_60) <- colnames(daily_returns)
```

```{r dplyr,warning=FALSE,message=FALSE}
require(dplyr)
require(tidyr)
```

# Introduction

## Setup

- Last data date: `r last_data_date`
- Reference symbols: SPY, TLT
- NO LONGER USING DATA FEED: Yahoo! Finance
- Data feed: Quandl CBOE, Merrill-Lynch


# Biggest Movers

## Biggest Moves 30-Days

```{r bigmoves-gain}
biggest <- 6
df <- data.frame(cumprod(1 + daily_returns_30))
odf <- sort(rank(tail(df,1)),decreasing=TRUE)
bignames <- names(odf)[1:biggest]

df <- df %>% 
  mutate(Date=as.Date(rownames(df))) %>%
  select(which(names(df) %in% bignames),Date) %>%
  gather(Product,Return,-Date)
p <- ggplot(df,aes(x=Date,y=(Return-1),colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL) +
  theme(legend.position="right") +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Biggest Gainers Last 30 Days Cumulative Return")
direct.label(p)
```

----

```{r,bigmoves-loss}
biggest <- 6
df <- data.frame(cumprod(1 + daily_returns_30))
odf <- sort(rank(tail(df,1)),decreasing=FALSE)
bignames <- names(odf)[1:biggest]

df <- df %>% 
  mutate(Date=as.Date(rownames(df))) %>%
  select(which(names(df) %in% bignames),Date) %>%
  gather(Product,Return,-Date)
p <- ggplot(df,aes(x=Date,y=(Return-1),colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL) +
  theme(legend.position="right") +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Biggest Losers Last 30 Days Cumulative Return")
direct.label(p)
```


# Macro Performance

## Macro Funds

```{r last-60-days-macro}
df <- data.frame(cumprod(1 + daily_returns_60[,macro_tickers]))
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Return,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=(Return-1),colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Macro Last 60 Days Cumulative Return")
direct.label(p)
```

----

```{r last-60-days-macro-relative}
df <- data.frame( relative_spy_60[,macro_tickers] )
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Return,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=Return-1,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Relative Return (SPY)") +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Macro Last 60 Days Cumulative Relative Return")
direct.label(p)
```

----

```{r last-60-days-macro-relative-bar}
sr <- relative_spy_60[,macro_tickers] - 1
df <- data.frame(tail(sr,1))
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% select(-which(colnames(df)=='SPY')) %>% gather(Product,Return,-Date)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  scale_y_continuous(labels=percent_format()) +
  labs(x=NULL,y="Relative Return (%, SPY)") +
  ggtitle("Macro Last 60 Days Cumulative Relative Return")
p
```

----

```{r,macro-relative-multibar}
sr30 <- relative_spy_30[,macro_tickers] - 1
sr60 <- relative_spy_60[,macro_tickers] - 1
df30 <- data.frame(tail(sr30,1))
df60 <- data.frame(tail(sr60,1))
df30$Period <- "30 Days"
df60$Period <- "60 Days"
df30 <- df30 %>% select(-which(colnames(df30)=='SPY')) %>% gather(Product,Return,1:(ncol(df30)-2))
df60 <- df60 %>% select(-which(colnames(df60)=='SPY')) %>% gather(Product,Return,1:(ncol(df60)-2))
df <- rbind(df30,df60)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  facet_grid(.~Period) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Macro Cumulative Relative Return by Period") +
  labs(x=NULL,y="Relative Return (%, SPY)")
p
```

# Model Performance

## Bull Model Performance

```{r last-60-days-bull}
df <- data.frame(cumprod(1 + daily_returns_60[,bull_tickers]))
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Return,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=Return-1,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bull Model Last 60 Days Cumulative Return")
direct.label(p)
```

----

```{r last-60-days-bull-relative}
sr <- relative_spy_60[,bull_tickers]
df <- data.frame(sr)
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Return,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=Return-1,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Relative Return (SPY)") +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bull Last 60 Days Cumulative Relative Return")
direct.label(p)
```

----

```{r last-60-days-bull-relative-bar}
sr <- relative_spy_60[,bull_tickers] -1
df <- data.frame(tail(sr,1))
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Return,-Date)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  labs(x=NULL,y="Relative Return (%, SPY)") +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bull Last 60 Days Cumulative Relative Return")
p
```

----

```{r bull-relative-multibar}
sr30 <- relative_spy_30[,bull_tickers] -1
sr60 <- relative_spy_60[,bull_tickers] -1
df30 <- data.frame(tail(sr30,1))
df60 <- data.frame(tail(sr60,1))
df30$Period <- "30 Days"
df60$Period <- "60 Days"
df30 <- df30 %>% gather(Product,Return,1:(ncol(df30)-2))
df60 <- df60 %>% gather(Product,Return,1:(ncol(df60)-2))
df <- rbind(df30,df60)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  facet_grid(.~Period) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bull Relative Return by Period") +
  labs(x=NULL,y="Relative Return (%,SPY)")
p
```

----

```{r bull-absolute-multibar}
sr30 <- daily_returns_30[,bull_tickers]
sr60 <- daily_returns_60[,bull_tickers]
sr30 <- Return.cumulative(sr30)
sr60 <- Return.cumulative(sr60)
df30 <- data.frame(sr30)
df60 <- data.frame(sr60)
df30$Period <- "30 Days"
df60$Period <- "60 Days"
df30 <- df30 %>% gather(Product,Return,1:(ncol(df30)-2))
df60 <- df60 %>% gather(Product,Return,1:(ncol(df60)-2))
df <- rbind(df30,df60)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  facet_grid(.~Period) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bull Absolute Return by Period") +
  labs(x=NULL,y="Period Return (%)")
p
```
----

## Bear Model Performance

```{r last-60-days-bear}
df <- data.frame(cumprod(1 + daily_returns_60[,bear_tickers]))
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Return,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=Return-1,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bear Model Last 60 Days Cumulative Return")
direct.label(p)
```

----

```{r last-60-days-bear-relative}
sr <- relative_spy_60[,bear_tickers]
df <- data.frame(sr)
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Return,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=Return-1,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Relative Return (SPY)") +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bear Last 60 Days Cumulative Relative Return")
direct.label(p)
```

----

```{r last-60-days-bear-relative-bar}
sr <- relative_spy_60[,bear_tickers] -1
df <- data.frame(tail(sr,1))
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% select(-which(colnames(df)=='SPY')) %>% gather(Product,Return,-Date)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  labs(x=NULL,y="Relative Return (%, SPY)") +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bear Last 60 Days Cumulative Relative Return")
p
```

----

```{r bear-relative-multibar}
sr30 <- relative_spy_30[,bear_tickers] -1
sr60 <- relative_spy_60[,bear_tickers] -1
df30 <- data.frame(tail(sr30,1))
df60 <- data.frame(tail(sr60,1))
df30$Period <- "30 Days"
df60$Period <- "60 Days"
df30 <- df30 %>% gather(Product,Return,1:(ncol(df30)-2))
df60 <- df60 %>% gather(Product,Return,1:(ncol(df60)-2))
df <- rbind(df30,df60)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  facet_grid(.~Period) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bear Relative Return by Period") +
  labs(x=NULL,y="Relative Return (%,SPY)")
p
```

----

```{r bear-absolute-multibar}
sr30 <- daily_returns_30[,bear_tickers]
sr60 <- daily_returns_60[,bear_tickers]
sr30 <- Return.cumulative(sr30)
sr60 <- Return.cumulative(sr60)
df30 <- data.frame(sr30)
df60 <- data.frame(sr60)
df30$Period <- "30 Days"
df60$Period <- "60 Days"
df30 <- df30 %>% gather(Product,Return,1:(ncol(df30)-2))
df60 <- df60 %>% gather(Product,Return,1:(ncol(df60)-2))
df <- rbind(df30,df60)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  facet_grid(.~Period) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Bear Absolute Return by Period") +
  labs(x=NULL,y="Period Return (%)")
p
```

----

## Basket Model Performance

```{r last-60-days-basket}
df <- data.frame(cumprod(1 + daily_returns_60[,basket_tickers]))
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Return,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=Return-1,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Basket Model Last 60 Days Cumulative Return")
direct.label(p)
```

----

```{r last-60-days-basket-relative}
sr <- relative_tlt_60[,basket_tickers]
df <- data.frame(sr)
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Return,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=Return-1,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Relative Return (TLT)") +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Basket Last 60 Days Cumulative Relative Return")
direct.label(p)
```

----

```{r last-60-days-basket-relative-bar}
sr <- relative_tlt_60[,basket_tickers] -1 
df <- data.frame(tail(sr,1))
df <- df %>% mutate(Date=as.Date(rownames(df))) %>% select(-which(colnames(df)=='TLT')) %>% gather(Product,Return,-Date)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  labs(x=NULL,y="Relative Return (%, TLT)") +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Basket Last 60 Days Cumulative Relative Return")
p
```

----

```{r basket-relative-multibar}
sr30 <- relative_tlt_30[,basket_tickers] -1
sr60 <- relative_tlt_60[,basket_tickers] -1
df30 <- data.frame(tail(sr30,1))
df60 <- data.frame(tail(sr60,1))
df30$Period <- "30 Days"
df60$Period <- "60 Days"
df30 <- df30 %>% select(-which(colnames(df30)=='TLT')) %>% gather(Product,Return,1:(ncol(df30)-2))
df60 <- df60 %>% select(-which(colnames(df60)=='TLT')) %>% gather(Product,Return,1:(ncol(df60)-2))
df <- rbind(df30,df60)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  facet_grid(.~Period) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Basket Relative Return by Period") +
  labs(x=NULL,y="Relative Return (%,TLT)")
p
```

----

```{r basket-absolute-multibar}
sr30 <- daily_returns_30[,basket_tickers]
sr60 <- daily_returns_60[,basket_tickers]
sr30 <- Return.cumulative(sr30)
sr60 <- Return.cumulative(sr60)
df30 <- data.frame(sr30)
df60 <- data.frame(sr60)
df30$Period <- "30 Days"
df60$Period <- "60 Days"
df30 <- df30 %>% select(-which(colnames(df30)=='TLT')) %>% gather(Product,Return,1:(ncol(df30)-2))
df60 <- df60 %>% select(-which(colnames(df60)=='TLT')) %>% gather(Product,Return,1:(ncol(df60)-2))
df <- rbind(df30,df60)
p <- ggplot(df,aes(x=reorder(Product,desc(Return)),Return,fill=Product)) +
  geom_bar(stat="identity",position="dodge") +
  theme(legend.position="off") +
  facet_grid(.~Period) +
  scale_y_continuous(labels=percent_format()) +
  ggtitle("Basket Absolute Return by Period") +
  labs(x=NULL,y="Period Return (%)")
p
```

# Volatility

## Equity Index Volatility

```{r volatility}
vix <- Cl(get("VIX",envir=exchange_data))
colnames(vix) <- "VIX"
vxst <- Cl(get("VXST",envir=exchange_data))
colnames(vxst) <- "VXST"
vxmt <- Cl(get("VXMT",envir=exchange_data))
colnames(vxmt) <- "VXMT"

spy <- Cl( get("SPY",envir=exchange_data) )
colnames(spy) <- "SPY"

df <- data.frame( xts::last( cbind(vix, vxmt, vxst, spy ), "90 days")) 

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
df$Panel <- "Volatility"
df$Panel[which(df$Product=="SPY")] <- "ETF"

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Volatility Value and Index Price") +
  ggtitle("CBOE Volatility Index Last 90 Days") +
  facet_grid(Panel~.,scales="free_y")
direct.label(p)

```

----

```{r skew}
skew <- get("SKEW",envir=exchange_data)
colnames(skew) <- "SKEW"
skew$MA50 <- SMA(skew$SKEW,n=50)

df.xts <- xts::last(skew,"90 days")
sf.xts <- Cl(xts::last( get("SPY",envir=exchange_data), "90 days") )
colnames(sf.xts) <- "SPY"
df <- data.frame(cbind(df.xts,sf.xts))

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
df$Panel <- "Skew Index"
df$Panel[which(df$Product=="SPY")] <- "ETF"

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Skew Value and Index Price") +
  ggtitle("CBOE Volatility Skew Last 90 Days") +
  facet_grid(Panel~.,scales="free_y")
direct.label(p)

```

----

```{r lovol}
lovol <- Cl(get("LOVOL",envir=exchange_data))
colnames(lovol) <- "LOVOL"
lovol$MA50 <- SMA(lovol$LOVOL,n=50)

df <- data.frame( xts::last(lovol,"90 days") )

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Index Value") +
  ggtitle("CBOE Low Volatility Index Last 90 Days")
direct.label(p)

```

----

```{r eemvol}
vxeem <- Cl(get("VXEEM",envir=exchange_data))
colnames(vxeem) <- "VXEEM"
vxeem$MA50 <- SMA(vxeem$VXEEM,n=50)

df.xts <- xts::last(vxeem,"90 days")
ef.xts <- Cl(xts::last( get("EEM",envir=exchange_data), "90 days") )
colnames(ef.xts) <- "EEM"
df <- data.frame(cbind(df.xts,ef.xts))

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
df$Panel <- "Volatility"
df$Panel[which(df$Product=="EEM")] <- "ETF"

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Volatility Value and Index Price") +
  ggtitle("CBOE Emerging Market Volatility Index Last 90 Days") +
  facet_grid(Panel~.,scales="free_y")
direct.label(p)

```

----

```{r gldvol}
gvz <- get("GVZ",envir=exchange_data)
colnames(gvz) <- "GVZ"
gvz$MA50 <- SMA(gvz$GVZ,n=50)

df.xts <- xts::last(gvz,"90 days")
gf.xts <- Cl(xts::last( get("GLD",envir=exchange_data), "90 days") )
colnames(gf.xts) <- "GLD"
df <- data.frame(cbind(df.xts,gf.xts))

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
df$Panel <- "Volatility"
df$Panel[which(df$Product=="GLD")] <- "ETF"

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Volatility Value and ETF Price") +
  ggtitle("CBOE Gold ETF Volatility Index Last 90 Days") +
  facet_grid(Panel~.,scales="free_y")
direct.label(p)

```

# Options Market

## Put/Call Ratios

```{r indexop}
SPXPC <- get("SPXPC",envir=exchange_data)

# CBOE/SPX_PC
# CBOE/VIX_PC
# CBOE/ETP_PC
# CBOE/EQUITY_PC
# CBOE/INDEX_PC
# CBOE/TOTAL_PC
# CBOE/TOTAL_PC_ARCHIVE  2003-10-17 to 2012-06-07
# CBOE/INDEX_PC_ARCHIVE  2003-10-16 to 2012-06-07
# CBOE/EQUITY_PC_ARCHIVE 2003-10-17 to 2012-06-07
# CBOE/COMBINED_PC_ARCHIVE  1995-09-27 to 2003-12-31 (TPC, IPC, EPC only (mislabeled))
# CBOE/PUT put write index

SPXPC <- SPXPC[,1]
colnames(SPXPC) <- "SPX"
SPXPC$MA10 <- SMA(SPXPC$SPX,n=10)
SPXPC.mean <- mean(SPXPC,na.rm=TRUE)
SPXPC.sd <- sd(SPXPC,na.rm=TRUE)



df <- data.frame( xts::last(SPXPC,"90 days") )

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Put-Call Ratio (Historical Mean. 1-Sigma)") +
  ggtitle("CBOE S&P 500 Index Put-Call Ratio Last 90 Days") +
  geom_hline(yintercept = SPXPC.mean, color="darkgray" ) +
  geom_hline(yintercept = SPXPC.mean + SPXPC.sd, color="darkgray", linetype="dotted") +
  geom_hline(yintercept = SPXPC.mean - SPXPC.sd, color="darkgray", linetype="dotted")
direct.label(p)

```

----

```{r mixpc}

EPC <- get("EQUITY_PC",envir=exchange_data)
IPC <- get("INDEX_PC",envir=exchange_data)
TPC <- get("TOTAL_PC",envir=exchange_data)

EPC <- EPC[,4] # cvol, pvol, tvol, ratio
colnames(EPC) <- "EPC"
IPC <- IPC[,4] # cvol, pvol, tvol, ratio
colnames(IPC) <- "IPC"
TPC <- TPC[,4] # cvol, pvol, tvol, ratio
colnames(TPC) <- "TPC"

EPC$MA5 <- SMA(EPC,n=5)
IPC$MA5 <- SMA(IPC,n=5)
TPC$MA5 <- SMA(TPC,n=5)

sf.xts <- Cl( get("SPY",envir=exchange_data) )

df.xts <- cbind(EPC$MA5,IPC$MA5,TPC$MA5,sf.xts)
colnames(df.xts) <- c("Equity","Index","Total","SPY")
df <- data.frame( xts::last(df.xts ,"90 days") )

# peaks.xts <- xts::last(df.xts[findPeaks(df.xts$Index,thresh=0.1),],"90 days")
# peaks.df <- data.frame( peaks.xts )
# peaks.df <- peaks.df %>% mutate(Date=as.Date(rownames(peaks.df)))

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
df$Panel <- "Put-Call Ratios"
df$Panel[which(df$Product=="SPY")] <- "ETF"

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Put-Call Ratio (5-Day MA) and Price ($)") +
  ggtitle("CBOE S&P 500 Put-Call Ratio Last 90 Days") +
  facet_grid(Panel~.,scales="free_y")

direct.label(p)
```

---

```{r tpchist}
# CCHA range 1995-09-27 to 2003-12-31 columns TPCR, IPCR, EPCR (mislabeled)
# TPCA range 2003-10-17 to 2012-06-07  
# TPC  range 2006-11-01 to present
CCHA <- get("CCHA",envir=exchange_data)
TPCA <- get("TPCA",envir=exchange_data)
TPC <- get("TPC",envir=exchange_data)
colnames(CCHA) <- c("Total","Index","Equity")
colnames(TPCA) <- c("Call","Put","Volume","Total")
colnames(TPC) <- c("Call","Put","Volume","Total")
total.xts <- rbind(CCHA["/2003-12-31","Total"],
                   TPCA["2004-01-01/2006-10-30","Total"],
                   TPC["2006-11-01/","Total"])
total.xts$MA30 <- SMA(total.xts$Total,n=30)
sf.xts <- Cl(get("SPY",envir=exchange_data))
colnames(sf.xts) <- "SPY"
df.xts <- cbind(total.xts,sf.xts)
df <- data.frame(xts::last(df.xts,"5 years"))

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date, -Total)
df$Panel <- "Total Put-Call Ratio"
df$Panel[which(df$Product=="SPY")] <- "SPY"

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Total Put-Call Ratio") +
  ggtitle("CBOE S&P 500 Put-Call Ratio History") +
  facet_grid(Panel~.,scales="free_y")

direct.label(p)

```

---

```{r tpcrsi}
CCHA <- get("CCHA",envir=exchange_data)
TPCA <- get("TPCA",envir=exchange_data)
TPC <- get("TPC",envir=exchange_data)
colnames(CCHA) <- c("Total","Index","Equity")
colnames(TPCA) <- c("Call","Put","Volume","Total")
colnames(TPC) <- c("Call","Put","Volume","Total")
total.xts <- rbind(CCHA["/2003-12-31","Total"],
                   TPCA["2004-01-01/2006-10-30","Total"],
                   TPC["2006-11-01/","Total"])
total.xts$MA30 <- SMA(total.xts$Total,n=30)
sf.xts <- Cl(get("SPY",envir=exchange_data))
colnames(sf.xts) <- "SPY"

sf.xts$RSI <- TTR::RSI(sf.xts$SPY,n=14)
total.xts$RSI <- TTR::RSI(total.xts$MA30,n=14)

df.xts <- cbind(total.xts$RSI,sf.xts$RSI)
colnames(df.xts) <- c("Total","SPY")

df <- data.frame(xts::last(df.xts,"3 years"))

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
df$Panel <- "TPCR MA30 RSI14"
df$Panel[which(df$Product=="SPY")] <- "SPY RSI14"

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Total Put-Call Ratio and Price") +
  ggtitle("CBOE S&P 500 Put-Call Ratio RSI Comparison") +
  facet_grid(Panel~.,scales="free_y")

direct.label(p)

```

# Corporate Debt

## Merrill-Lynch Bond Indices


```{r oas}
MLAAOAS <- get("MLAAOAS",envir=exchange_data)
MLBOAS <- get("MLBOAS",envir=exchange_data)
MLHYOAS <- get("MLHYOAS",envir=exchange_data)
ml.xts <- cbind(MLAAOAS,MLBOAS,MLHYOAS)
colnames(ml.xts) <- c("AA","B","HY")

sf.xts <- Cl(get("SPY",envir=exchange_data))
colnames(sf.xts) <- "SPY"

df.xts <- cbind(ml.xts,sf.xts)

df <- data.frame(xts::last(df.xts,"12 months"))

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
df$Panel <- "Spread (%)"
df$Panel[which(df$Product=="SPY")] <- "ETF ($)"

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Option-Adjusted Spread and Price") +
  ggtitle("Corporate Bond Spread and Equity Price Comparison") +
  facet_grid(Panel~.,scales="free_y")

direct.label(p)

```

----

```{r yyy}
MLAAY <- get("MLAAY",envir=exchange_data)
MLBBY <- get("MLBBY",envir=exchange_data)
MLCCCY <- get("MLCCCY",envir=exchange_data)
ml.xts <- cbind(MLAAY,MLBBY,MLCCCY)
colnames(ml.xts) <- c("AA","BB","CCC")

sf.xts <- Cl(get("SPY",envir=exchange_data))
colnames(sf.xts) <- "SPY"

df.xts <- cbind(ml.xts,sf.xts)

df <- data.frame(xts::last(df.xts,"12 months"))

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)
df$Panel <- "Yield (%)"
df$Panel[which(df$Product=="SPY")] <- "ETF ($)"

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Corporate Bond Yield and Price") +
  ggtitle("Corporate Bond Yield and Equity Price Comparison") +
  facet_grid(Panel~.,scales="free_y")

direct.label(p)

```

# Correlation

## Rolling Correlation of Asset Class Returns


```{r monthly}
monthly_closing_prices <- closing_prices[endpoints(closing_prices,"months"),]
monthly_returns <- monthly_closing_prices / stats::lag(monthly_closing_prices) - 1
monthly_returns <- monthly_returns[-1]
monthly_returns[is.na(monthly_returns)] <- 0
```


```{r mcorr}
cdata <- monthly_returns[,c('SPY','AGG','DBC','EEM','GLD','UUP','VNQ')]

rcorr <- rollapply(cdata[,2:7], width=12, function(x) {
  cor(x,cdata[index(x),'SPY'])
  }, by=1, by.column=TRUE)

df <- data.frame(xts::last(rcorr,"36 months"))

df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date)

p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) +
  geom_line(size=stroke_size) +
  labs(x=NULL,y="Correlation of 12-Month Returns") +
  ggtitle("Rolling 12-Month Correlation of Price Returns with SPY") +
  scale_y_continuous(limits=c(-1,1)) +
  geom_hline(yintercept = 0, color="black", linetype="dashed")

direct.label(p)
```


<!-- # Futures Market -->

<!-- ## S&P 500 Futures Term Structure -->

<!-- ```{r esterm} -->
<!-- ES1 <- get("ES1",envir=exchange_data) -->
<!-- ES4 <- get("ES4",envir=exchange_data) -->
<!-- SPX <- quantmod::Ad(get("GSPC",envir=exchange_data)) -->
<!-- df.xts <- cbind(ES1,ES4,SPX) -->
<!-- colnames(df.xts) <- c("ES1","ES4","SPX") -->

<!-- df <- data.frame(na.locf(xts::last(df.xts,"24 months"))) -->
<!-- df$Ratio <- df$ES4 / df$ES1 -->
<!-- df <- df %>% mutate(Date=as.Date(rownames(df))) %>% gather(Product,Value,-Date) -->

<!-- df$Panel <- "Price ($)" -->
<!-- df$Panel[which(df$Product=="Ratio")] <- "Ratio (M4/M1)" -->

<!-- p <- ggplot(df %>% na.omit,aes(x=Date,y=Value,colour=Product)) + -->
<!--   geom_line(size=stroke_size) + -->
<!--   labs(x=NULL,y="Futures and Index Price ($)") + -->
<!--   ggtitle("S&P-500 Continuous Futures and Index Price") + -->
<!--   facet_grid(Panel~.,scales="free_y") -->
<!-- direct.label(p) -->
<!-- ``` -->

       
